Association between trauma severity models and opportunities for improvement:

### 2022-10-18 manuscript.Rmd
fix?
plots actually work

---
title: 'Association between trauma severity models and opportunities for improvement:
  A retrospective cohort study'
author: "Victoria Witthoff"
output:
  html_document: default
  pdf_document: default
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
always_allow_html: true
---

@@

The odds ratio for TRISS was `r t.stats[['or']]` (95% CI: `r t.stats[['or.ci']]`, p-value: `r t.stats[['or.p']]`). When plotting the ROC, the AUC was `r t.stats[['auc']]` (95% CI: `r t.stats[['auc.ci']][1]`-`r t.stats[['auc.ci']][3]`). The odds ratio for NORMIT was `r n.stats[['or']]` (95% CI: `r n.stats[['or.ci']]`, p-value: `r n.stats[['or.p']]`). When plotting the ROC, the AUC was `r n.stats[['auc']]` (95% CI: `r n.stats[['auc.ci']][1]`-`r n.stats[['auc.ci']][3]`).

>>>>

---
title: 'Association between trauma severity models and opportunities for improvement:
  A retrospective cohort study'
author: "Victoria Witthoff"
output:
  html_document: default
  pdf_document: default
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
always_allow_html: true
editor_options: 
   chunk_output_type: inline
---

@@

The odds ratio for TRISS was `r t.stats[['or']]` (95% CI: `r t.stats[['or.ci']]`, p-value: `r t.stats[['or.p']]`). When plotting the ROC, the AUC was `r t.stats[['auc']]` (95% CI: `r t.stats[['auc.ci']][1]`-`r t.stats[['auc.ci']][3]`). The integrated calibration index for TRISS was `r t.stats[['ici']]`.

The odds ratio for NORMIT was `r n.stats[['or']]` (95% CI: `r n.stats[['or.ci']]`, p-value: `r n.stats[['or.p']]`). When plotting the ROC, the AUC was `r n.stats[['auc']]` (95% CI: `r n.stats[['auc.ci']][1]`-`r n.stats[['auc.ci']][3]`). The integrated calibration index for NORMIT was `r n.stats[['ici']]`.

`r t.plot.roc`
`r t.plot.acc`

`r n.plot.roc`
`r n.plot.acc`
